Species richness and network structure jointly drive total biomass and its temporal stability in fish communities

### 2020-12-17 manuscript/bef_stability/manuscript.Rmd
Decrease to 5000 words:
8391 - 21 - 237 - 2730 - 251 - 151

- Number of words:
  - Abstract: 151
  - Main text: 5535

@@

Because their trophic interactions are well known, stream fish communities
constitute a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic interactions are
difficult to measure in natural conditions, a substantial body of literature
supports that they can be inferred through body size and diet informations
[@jennings_weak_2001; @gravel_inferring_2013; @brose_predator_2019]. Especially
in stream communities, including fishes, @brose_predator_2019 found that the
prediction of predator-prey trophic interactions based on body size ratio was
far better in stream ecosystems than in other aquatic and terrestrial
ecosystems. Lastly, most of the diversity-biomass and diversity-stability
relationships, have been assessed in terrestrial ecosystems while there is a
evident need to test such relationships in a variety of ecosystem types.

Our aim is to document the relationships among species richness, foodweb
structure, total biomass and its temporal stability in natural communities. To
do so, we used the ONEMA dataset consisting in a standardized sampling of fish
communities in French streams [@edeline_ecological_2013]. We selected 99 sites
that have been sampled for more than 10 years spanning on the 1995-2018 period. We
inferred 1496 interaction networks, based on body size and diet. We question
whether species richness, connectance and average trophic level increase,
decrease or are unrelated to total biomass and its temporal stability. We
further question whether the species richness, connectance, and average trophic
level have antagonistic or mutual effect on total biomass and its temporal
stability. Finally, we question if ecosystem size and average temperature
increase total biomass and its temporal stability.

@@

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. Species identity allowed to
differentiate between piscivorous and non piscivorous species, to know which
resources the trophic species are feeding on and to know the minimum size at
which a piscivorous species begin to feed on fishes. The ontogenic fish diet
database was filled according to fishbase and literature (appendix A, Table S2). Each
fish species had two or three life stages which are delimited by a body size
range (Fig. S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Fig. S2).

@@

The structural equation models were based on Gaussian linear models. All variables
except the connectance and average trophic level
were logged to fulfill model assumptions (see residual plots and data
transformation in Fig. S5 and S6, Table S5). We set the seven
hydrographic basins as a random effect on the intercept of the linear models to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table S6). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). The paths whose
slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
path values are presented in Table S7 and S8).

Indirect effects on total biomass and its temporal stability
were computed by multiplying slopes along the path. As an example, if we consider
$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
r_{BC}$.  Only significant direct slopes were entered in the calculation of
indirect effects. Finally total effects were computed as the sum
of direct and indirect effects.

@@

The structural equation models explained a large part of the variation
of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
trophic level ($R^2 =
.11$, Fig. \@ref(fig:sem-plot) B and D). We found that species richness had a
significant negative effect on mean trophic level ($r_\delta = 
`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Fig.
\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species richness went 
through network structure.

>>>>

- Number of words:
  - Abstract: 151
  - Main text: 4980

@@

Because their trophic interactions are well known, stream fish communities
constitute a good model to study the effects of network structure on total
biomass and its temporal stability. Despite that fish trophic interactions are
difficult to measure in natural conditions, a substantial body of literature
supports that they can be inferred through body size and diet informations
[@jennings_weak_2001; @gravel_inferring_2013], especially
in stream communities including fishes [@brose_predator_2019]. Lastly, most of
the diversity-biomass and diversity-stability relationships, have been assessed
in terrestrial ecosystems while there is a evident need to test such
relationships in a variety of ecosystem types.

Our aim is to document the relationships among species richness, foodweb
structure, total biomass and its temporal stability in natural communities. To
do so, we used the ONEMA dataset consisting in a standardized sampling of fish
communities in French streams [@edeline_ecological_2013]. We selected 99 sites
that have been sampled for more than 10 years spanning on the 1995-2018 period. We
inferred 1496 interaction networks, based on body size and diet. We question
whether species richness, connectance and average trophic level are related or
not to total biomass and its temporal stability. We further question whether
species richnes and foodweb structure have antagonistic or mutual effect on
total biomass and its temporal stability. Finally, we question how ecosystem size
and average temperature are related to total biomass and its temporal stability.

@@

The feeding interactions of a fish node, i.e. a trophic species, were determined
by both its species identity and its body size. The ontogenic fish diet
database was filled according to fishbase and literature (appendix A, Table S2). Each
fish species had two or three life stages which are delimited by a body size
range (Fig. S2). The life stage of a fish trophic species was determined with
the center of its body size range, hereafter midpoint (Fig. S2).

@@

The structural equation models were based on Gaussian linear models. All variables
except the connectance and average trophic level
were logged to fulfill model assumptions (see residual plots and data
transformation in Fig. S5 and S6, Table S5). We set the seven
hydrographic basins as a random effect on the intercept to
account for their heterogeneity. We checked for the absence of multicollinearity 
with Variance Inflation Factor (VIF, Table S6). The slopes reported
in the main text were standardized in order to compare their magnitude ($r_\delta
= \beta \frac{\sigma_x}{\sigma_y}$, $\beta$ being the unstandardized slope,
$\sigma_x$ and $\sigma_y$ being respectively the standard deviation of the
predictive variable $x$ and of the response variable $y$). The paths whose
slope had a $P$ value inferior to $0.05$ were reported in the main text, all the
path values are presented in Table S7 and S8.

Indirect effects on total biomass and its temporal stability
were computed by multiplying slopes along the path. As an example, if we consider
$A \to B \to C$, the indirect effect of A on C is equal to $r_{AB} \times
r_{BC}$. Only significant direct slopes were entered in the calculation of
indirect effects. Total effects were computed as the sum
of direct and indirect effects.

@@

The structural equation models explained a large part of the variation
of species richness, connectance, synchrony, $\overline{CV_{sp}}$ and total
biomass (resp. $R^2 = .43$, $.38$, $.46$, $.47$ and $.32$) but less so for mean
trophic level ($R^2 =
.11$, Fig. \@ref(fig:sem-plot) B and D). Species richness had a
significant negative effect on mean trophic level ($r_\delta = 
`r rich_on_tlvl`$) and connectance ($r_\delta = `r rich_on_ct`$, Fig.
\@ref(fig:sem-plot) B and D), meaning that a part of the effects of species
richness went through network structure.
